Supplementary material

### 2021-12-13 submission/supplement.rmd
add sections

For the second part linear and quadratic deviations from the
assumption of constant relative effect are considered. We also
consider different intensity levels of these deviations. The settings
for these deviations are defined in Table \@ref(tab:tab1) and result
in the effects of Figure \@ref(fig:fig1).

```{r fig1, echo=FALSE, fig.cap="Linear and quadratic deviations from the base-case scenario of constant relative effect (OR=0.8)", fig.show="hold", out.width = '50%'}
knitr::include_graphics(here::here("figures/deviate_linear_08.png"))
knitr::include_graphics(here::here("figures/deviate_quadratic_08.png"))
```

In Figure \@ref(fig:fig2) the absolute benefits observed based on different
settings are presented. The base-case scenario is also presented as a reference.

```{r fig2, echo=FALSE, fig.cap="Linear and quadratic deviations from the base-case scenario of constant relative effect (OR=0.8)", fig.show="hold", out.width = '50%'}
knitr::include_graphics(here::here("figures/deviate_linear_absolute_08.png"))
knitr::include_graphics(here::here("figures/deviate_quadratic_absolute_08.png"))
```

Finally, we consider 3 additional scenarios of interaction of
individual covariates with treatment. These scenarios include a 4 weak
interactions ($\text{OR}_{t_x=1} / \text{OR}_{t_x=0}=0.82$), 4 strong
interactions ($\text{OR}_{t_x=1} / \text{OR}_{t_x=0}=0.61$), and 2
weak and 2 strong interactions (Table \@ref(tab:tab2)).

@@

```{r tab1, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
 asd <- read_csv(
  here("data/processed/analysisIds.csv")
) %>%
  select(-"type")
kableExtra::kable(
  asd,
  format = "latex",
  escape = FALSE,
  longtable   = TRUE,
  align       = "r",
  booktabs    = TRUE,
  caption     = "",
  col.names   = c(
    "Scenario",
    "Base",
    "N",
    "AUC",
    "Treatment-related harm",
    paste0("b", 0:8),
    paste0("g", 0:2),
    "c",
    "Average benefit"
  ),
  digits      = 2,
  format.args = list(
    big.mar      = ",",
    decimal.mark = "."
  )
) %>%
  kableExtra::landscape() %>%
  kableExtra::add_header_above(
    c(
      "Analysis ID"           = 5,
      "Baseline risk"         = 9,
      "True treatment effect" = 4
      )
  ) %>%
  kableExtra::kable_styling(font_size = 7)
```

>>>>

For the second part linear, quadratic and non-monotonic deviations
from the assumption of constant relative effect are considered. We
also consider different intensity levels of these deviations. Finally,
constant absolute treatment-related harms are introduced,
i.e. positive ($0.25\times\text{true average benefit}$), strong
positive ($0.50\times\text{true average benefit}$) and negative
($-0.25\times\text{true average benefit}$; i.e. constant absolute
treatment-related benefit). In case of true absent treatment effects,
treatment-related harms are set to $1\%, 2\%$ and $-1\%$ for
positive, strong positive and negative setting, respectively. The
settings for these deviations are defined in Table \@ref(tab:tab1).

@@

```{r tab1, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
 asd <- read_csv(
  here("data/processed/analysisIds.csv")
) %>%
  select(-"type")
kableExtra::kbl(
  asd,
  format = "latex",
  escape = FALSE,
  longtable   = TRUE,
  align       = "r",
  booktabs    = TRUE,
  caption     = "Scenario settings of the entire simulation study.",
  col.names   = c(
    "Scenario",
    "Base",
    "N",
    "AUC",
    "Treatment-related harm",
    paste0("b", 0:8),
    paste0("g", 0:2),
    "c",
    "Before harms",
    "After harms"
  ),
  linesep = c('', '', '', '\\addlinespace'),
  digits      = 2,
  format.args = list(
    big.mar      = ",",
    decimal.mark = "."
  )
) %>%
  kableExtra::landscape() %>%
  kableExtra::add_header_above(
    c(
      "Analysis ID"           = 5,
      "Baseline risk"         = 9,
      "True treatment effect" = 4,
      "Benefit"               = 2
      )
  ) %>%
  kableExtra::kable_styling(font_size = 7)
```

# Adaptive model selection frequencies

```{r adaptiveBase, cache=TRUE, echo=FALSE, fig.cap="Adaptive model selection rates for the base case scenario true prediction AUC of 0.75, sample size of 4250", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/selected_model_adaptive_base.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r adaptiveSampleSize, cache=TRUE, echo=FALSE, fig.cap="Adaptive model selection rates for sample size of 17000.", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/selected_model_adaptive_sample_size.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r adaptiveAuc, cache=TRUE, echo=FALSE, fig.cap="Adaptive model selection rates for true prediction AUC of 0.85.", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/selected_model_adaptive_auc.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

\newpage

# Strong relative treatment effect

Here we present the root mean squared error of the considered methods
using strong constant relative treatment effect ($\text{OR}=0.5$) as
the reference. Again, the same sample size and prediction performance
settings were considered along with the same settings for linear,
quadratic and non-monotonic deviations from the base case scenario of
constant relative treatment effects are considered. All results can be found at [https://arekkas.shinyapps.io/simulation_viewer/](https://arekkas.shinyapps.io/simulation_viewer/).

```{r rmseHighBase, cache=TRUE, echo=FALSE, fig.cap="RMSE high effect base", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_high_base.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r rmseHighSampleSize, cache=TRUE, echo=FALSE, fig.cap="RMSE high effect sample size", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_high_sample_size.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r rmseHighAuc, cache=TRUE, echo=FALSE, fig.cap="RMSE high effect auc", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_high_auc.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```
